Constant-round Blind Classical Verification of Quantum Sampling

### 2021-02-19 paper.tex
Sync Overleaf changes

\maketitle
%\thispagestyle{plain}

@@

In a recent breakthrough, Mahadev constructed a classical verification of quantum computation (CVQC) protocol for a  classical client to delegate decision problems in $\BQP$ to an untrusted quantum prover under computational assumptions. In this work, we explore further the feasibility of CVQC with the more general \emph{sampling} problems in BQP and with the desirable \emph{blindness} property. We contribute affirmative solutions to both as follows. 
\begin{itemize}
\item  Motivated by the sampling nature of many quantum applications (e.g., quantum algorithms for machine learning and quantum supremacy tasks), we initiate the study of  CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$).  More precisely, in a CVQC protocol for a $\SampBQP$ problem, the prover and the verifier are given an input $x\in \zo^n$ and a quantum circuit $C$, and the goal of the classical client is to learn a sample from the output $z \leftarrow C(x)$ up to a small error, from its interation with an untrusted prover. We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Error} assumption.

>>>>

\date{}
\maketitle
%\thispagestyle{plain}

@@

In a recent breakthrough, Mahadev constructed a classical verification of quantum computation (CVQC) protocol for a  classical client to delegate decision problems in $\BQP$ to an untrusted quantum prover under computational assumptions. In this work, we explore further the feasibility of CVQC with the more general \emph{sampling} problems in BQP and with the desirable \emph{blindness} property. We contribute affirmative solutions to both as follows. 
\begin{itemize}
\item  Motivated by the sampling nature of many quantum applications (e.g., quantum algorithms for machine learning and quantum supremacy tasks), we initiate the study of  CVQC for \emph{quantum sampling problems} (denoted by $\SampBQP$).  More precisely, in a CVQC protocol for a $\SampBQP$ problem, the prover and the verifier are given an input $x\in \zo^n$ and a quantum circuit $C$, and the goal of the classical client is to learn a sample from the output $z \leftarrow C(x)$ up to a small error, from its interaction with an untrusted prover. We demonstrate its feasibility by constructing a four-message CVQC protocol for $\SampBQP$ based on the quantum \emph{Learning With Error} assumption.
